---
title: "EPID674 Epidemiologic Data Analysis using R"
subtitle: "Getting Started with R"
author: "Kelly Bakulski"
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document: default
  html_document: 
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 1, Getting Started with R


## Make your first R objects
```{r make objects}
#### Remarks or comments can be put behind the # symbol 
#### Anything from the # to the end of the line will be ignored by R  

x <- 4 # x is assigned the value of 4.
x # See what x is
y <- 7 # y is assigned the value of 7
x + y # See what x+y is
z <- x * (x + y) # z is assigned the value of x*(x+y)
z # See what z is
```


# Perform some calculations with 'x' and observe the results
```{r calculations on a vector}
x + 4
x - 3
x * 7
x / 10
x * x
x^2
x / x
x == x
```

# Assign a vector of integers from 1 to 4 to the object x, using multiple different functions
```{r make integer vector}
x <- 1:4 # This writes over the previous x object. No warning or error messages!
x
length(x) # length is a function for checking how long an object is
x <- seq(from=1, to=4, by=1) # Create a vector counting from 1 to 4 by 1
x
x <- c(1, 2, 3, 4) # Combine elements into a vector
x
x <- c(2, 3, 4, 1)
x
length(x)
y <- rep(7, times=4) # Create a vector with four 7's by rep() and assign it to y
y
```

# Make a character vector
```{r make character vector}
z <- c("UM", "SPH", "EPI", "Kelly")
z <- c("University of Michigan", "School of Public Health", "Epidemiology", "John Snow")
z
```

# What are the differences between ( ) and [ ] ?
```{r indexing vector}
length(z) # Rounded parentheses are for functions
z[3] # Square brackets are for looking in objects, this is also called "indexing"
z[2] # Find value based on position
z[1:3]

#Find positions meeting criteria
x<3 #Provides True/False for whether meets the criteria
which(x<3) #Finds the positions of the Trues

#Find values meeting criteria
x[x<3]
```

# Specify options in a function
```{r options in a function}
seq(from = 10, to = 23, by = 1) # count from 10 to 23 by 1
seq(from = 10, to = 23) # equivalent
seq(10, 23) # equivalent
seq(10, -3) # count from 10 to -3
seq(from = -1, to = 11, by = 3) # count from -1 to 11 by 3

#Note, you have all of the tools to complete homework 1
```


# Make your first data frame
```{r data frame}
# Combine x and y vectors by column into a data frame and assign it to an object called 'df'
df <- data.frame(x, y, z)
df # Look at df
df$x # Use $ to call up columns within data frames
df$y
```

# Index (look around) inside the data frame based on the position
```{r indexing data frame}
#Index based on position
df[3, 1] # structure: df[rows,columns]
df[4, ]
df[, 1]
df[c(1, 2, 3), ] # Read your R code from the inside out. Start with the innermost set of parentheses.
df[c(3, 1, 3), ]
df[c(FALSE, TRUE, TRUE, FALSE), ]
df[c(T, F, F, T), ]

#Index based on value
df$x>2 #Find a logical vector (True/False) of the rows that meet the value of interest (in this case x>2)
df[, 1] > 2 #Same as above
which(df[,1]>2) #Find rows that meet the criteria, similar to line above

df[df$x>2,] #Now show the rows that are True
df[df[, 1] > 2, ]  #Same as above
```

# Perform calculations on the data frame
```{r calculations data frame}
sum(df[, 1])
sum(x)
```

# Recode a value in the data frame based on the position
```{r recode}
df 
df[3, 2] <- 5 # recode a value
#What do you expect?
df #What do you get?
#Do they match?
```

# Remember to save your R script!
# To exit R 
```{r exit, eval=FALSE}
q()
```


