---
title: "EPID674 Epidemiologic Data Analysis using R"
subtitle: "Homework 1"
author: "Insert Your Name Here"
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1
## 1.  What is the boiling point of water (100 oC) in degrees F?

```{r problem_1}
#Insert your code for problem 1 here

```
Interpret your answer for problem 1 here


## 2.  What is today's temperature in degree C? (e.g. 77 oF)

```{r problem_2}
#Insert your code for problem 2 here

```
Interpret your answer for problem 2 here


## 3.  Make a vector ‘x’ as a series of even numbers from 2 to 20.  Make a vector ‘y’ as a series of integers running from 1 to 10. 
 Compute x+y, x-y, x*y, and x/y

```{r problem_3}
#Insert your code for problem 3 here

```
Interpret your answer for problem 3 here


## 4.  Compute the value of 1^2 + 2^2 + 3^2 + ... + 100^2

```{r problem_4}
#Insert your code for problem 4 here

```
Interpret your answer for problem 4 here
