---
title: "EPID674 Epidemiologic Data Analysis using R"
subtitle: "Homework 1"
author: "Insert Your Name Here"
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Problem 1A
## 1A.  What is the boiling point of water (100 oC) in degrees F?
```{r problem 1A}
#Insert your code for problem 1A here
```
#Interpret your answer for problem 1A here


## 1B.  What is today's temperature in degree C? (e.g. 77 oF)
```{r problem 1B}
#Insert your code for problem 1B here
```
#Interpret your answer for problem 1B here


## 2.  Make a vector ‘x’ as a series of even numbers from 2 to 20.  Make a vector ‘y’ as a series of integers running from 1 to 10. 
# Compute x+y, x-y, x*y, and x/y
```{r problem 2}
#Insert your code for problem 2 here
```
#Interpret your answer for problem 2 here


## 3.  Compute the value of 1^2 + 2^2 + 3^2 + ... + 100^2
```{r problem 3}
#Insert your code for problem 3 here
```
#Interpret your answer for problem 3 here
