---
title: "EPID674 Epidemiologic Data Analysis using R"
subtitle: "Homework 1"
author: "Kelly Bakulski"
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
format: html
editor: visual
---

# Problem 1

## 1. What is the boiling point of water (100 oC) in degrees F?

```{r}
#| label: promblem-1

9/5 * 100 + 32

```

The boiling point of water is `r 9/5*100+32` degrees F.

# Problem 2

## 2. What is today's temperature in degree C? (e.g. 77 oF)

```{r}
#| label: problem-2

(77 - 32) * 5 / 9 

```

Today’s temperature (assuming 77 degrees F) is `r (77 - 32) * 5 / 9` degrees C.

# Problem 3

## 3. Make a vector 'x' as a series of even numbers from 2 to 20. Make a vector 'y' as a series of integers running from 1 to 10.

Compute x+y, x-y, x\*y, and x/y

```{r}
#| label: problem-3

x <- c(2, 4, 6, 8, 10, 12, 14, 16, 18, 20)
#or 
x <- seq(2, 20, by=2)

y <- 1:10
#or
y <- seq(1, 10)

# compute x+y, x-y, x*y, and x/y
x + y

x - y

x * y

x / y

```

* The value of x + y is `r x + y`
* The value of x - y is `r x - y`
* The value of x times y is `r x * y`
* The value of x / y is `r x / y`

# Problem 4

## 4. Compute the value of 1\^2 + 2\^2 + 3\^2 + ... + 100\^2

```{r}
#| label: problem-4

z <- 1:100

z * z

sum(z * z)
```


The value of 1^2 + 2^2 + 3^2 + ... + 100^2 is `r sum(z*z)`
